\documentclass[12pt,-letter paper]{article}
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
\doublespacing
\singlespacing
\usepackage[none]{hyphenat}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{amsthm}
\interdisplaylinepenalty=2500
%\savesymbol{iint}
\usepackage{txfonts}
%\restoresymbol{TXF}{iint}
\usepackage{wasysym}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{txfonts}
\let\vec\mathbf{}
\usepackage{stfloats}
\usepackage{float}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
\usepackage{amssymb}
%\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{eenrc}
%\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
%\usepackage{listings}
\usepackage[latin1]{inputenc}
%%\usepackage{color}{   
%%\usepackage{lscape}
\usepackage{textcomp}
\usepackage{titling}
\usepackage{hyperref}
%\usepackage{fulbigskip}   
\usepackage{tikz}
\usepackage{graphicx}
\lstset{
  frame=single,
  breaklines=true
}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{siunitx}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tfrupee}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mwe} % for blindtext and example-image-a in example
\usepackage{wrapfig}
\graphicspath{{figs/}}
\providecommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\providecommand{\myvec}[1]{\ensuremath{\begin{bmatrix}#1\end{bmatrix}}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\begin{document}
\begin{enumerate}
\item Write the position vector of the point which divides the join of points with position vectors $ \overrightarrow{3a} -\overrightarrow{2b} $ and $ \overrightarrow{2a}+\overrightarrow{3b} $ in the ratio $ 2:1 $.
\item Write the number of vectors of unit length perpendicular to both the vectors:18 $ 
\vec{a} = 2\hat{i} + \hat{j} + 2\hat{k} \quad \text{and} \quad \vec{b} = \hat{j} + \hat{k}$
\item Find the vector equation of the plane with intercepts $3$, $-4$, and $2$ on the $x$, $y$, and $z$-axis, respectively.
\item If $x$$\epsilon N$ and $\myvec{x+3 & -2\\ -3x & 2x}=8$,then find the value of $x\cdot$.
\item Use elementary column operation $c_2 \rightarrow c_{2}+2c_{1}$ in the following  matrix  equation:\\ $\myvec{2 & 1 \\     2 & 0}=\myvec{3 & 1 \\ 2 & 0}\myvec{1 & 0 \\ -1 & 1}$
\item  Write the number of all possible matrices of order \(2\times 2\) with each entry $1$,$2$ or $3$.
\item Evaluate the integral : 
\begin{align*} 
\int_{0}^{\frac{\pi}{2}} \frac{\sin^2 x}{\sin x + \cos x} \, dx
\end{align*}
\item Evaluate the integral:
\begin{align*}
\int_{0}^\frac{3}{2}\left| x \cos(\pi x) \right| \, dx
\end{align*}
\item In a game a man wins  \rupee  $5$  for getting a number greater than $4$ and loses  \rupee $1$ otherwise, when a fair     die is thrown. The man decided to thrown the die thrice but to quit as and when he gets a number greater than $4$. Find the     expected value of the amount he wins/loses.
\item  A bag contains $4$ balls. Two balls are drawn at random $\brak{without replacement}$ and are found to be white. What     is the probability that all balls in the bag are white?
\item Evaluate the integral:                            \begin{align*}                                    
\int \frac{x^2}{x^4 + x^2 - 2} \, dx   
\end{align*}
\item If $x= a \sin 2t (1 + \cos 2t)$ and $y= b \cos 2t (1 - \cos 2t)$, Find $\frac{dy}{dx}$ at $ t = \frac{\pi}{4}$.
\item Find the coordinates of the point where the line through the points $ A(3,4,1) $ and $B(5,1,6)$ crosses the $xz$ plan    e. Also find the angle which this line make with the $xz$ plane.
\item Find \begin{align*}  
\int (3x+1)\sqrt {4-3x-2x^2} \, dx    
\end{align*}

\item The equation of tangent at $(2,3)$ on the curve $y^2=ax^3+b$ is $y=4x-5$. Find the values of $a$ and $b$.            
\item A trust invested some money in two type of bond. The first bond pays $10\%$ interest and second bond pay $12\%$ inter    est. The trust received \rupee $2$ ,$800$ as interest. However,if trust had interchanged money in bonds, they would have go    t \rupee $100$ less as interest. Using matrix method, find the amount invested by the trust. Interest received on this amou    nt will be given to Helpage India as donation. Which value is reflected in this question?
\end{enumerate}
\end{document}

