\documentclass[12pt,-letter paper]{article}
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
\doublespacing
\singlespacing
\usepackage[none]{hyphenat}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{commath}
\usepackage{amsthm}
\interdisplaylinepenalty=2500
%\savesymbol{iint}
\usepackage{txfonts}
%\restoresymbol{TXF}{iint}
\usepackage{wasysym}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{txfonts}
\let\vec\mathbf{}
\usepackage{stfloats}
\usepackage{float}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
\usepackage{amssymb}
%\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{eenrc}
%\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
%\usepackage{listings}
\usepackage[latin1]{inputenc}
%%\usepackage{color}{   
%%\usepackage{lscape}
\usepackage{textcomp}
\usepackage{titling}
\usepackage{hyperref}
%\usepackage{fulbigskip}   
\usepackage{tikz}
\usepackage{graphicx}
\lstset{
  frame=single,
  breaklines=true
}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{siunitx}
\let\vec\mathbf{}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tfrupee}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mwe} % for blindtext and example-image-a in example
\usepackage{wrapfig}
\graphicspath{{figs/}}
\providecommand{\mydet}[1]{\ensuremath{\begin{vmatrix}#1\end{vmatrix}}}
\providecommand{\myvec}[1]{\ensuremath{\begin{bmatrix}#1\end{bmatrix}}}
\providecommand{\cbrak}[1]{\ensuremath{\left\{#1\right\}}}
\providecommand{\brak}[1]{\ensuremath{\left(#1\right)}}
\begin{document}
\begin{enumerate}
\item Find the equation of plane passing through the points $A(,2,1)$, $B(4,2,-2)$ and $C(6,5,-1)$ and hence find the value of $\lambda $ for which $A(3,2,1)$, $B(4,2,-2)$ and $C(6,4,-1)$ and $D(\lambda,5,5)$ are coplanar.
\item Find the co-ordinates of the point where the line $\overrightarrow{r}=\hat{i}-2\hat{j}-3\hat{k}+\lambda(3\hat{i}+4\hat{j}+3\hat{k}$) meets the plane which is perpendicular to the vector $\overrightarrow{n}=\hat{i}+\hat{j}+3\hat{k}$ and at a distance of $\frac{4}{\sqrt{11}}$ of origin.
\item Given that vectors $\overrightarrow{a}$,$\overrightarrow{b}$,$\overrightarrow{c}$ form a triangle such that $\overrightarrow{a}=\overrightarrow{b}+\overrightarrow{c}$. Find P,Q,R,S such that area  of triangle is $5\sqrt{6}$ where $\overrightarrow{a}=p\hat{i}+q\hat{j}+r\hat{k}$ , $\overrightarrow{b}=s\hat{i}+3\hat{k}+4\hat{k}$ and $\overrightarrow{c}=3\hat{i}+\hat{j}-2\hat{k}$. 
\item There are two bags $A$ and $B$. Bag $A$ contains $3$ white and $4$ red balls whereas bag $B$ contains $4$ white and $3$ red balls. Three balls are drawn at random (without replacement) from one of the bags and are found to be two white and one red. Find the probability that these were drawn from bag $B$.
\item Ishan wants to donate a rectangular plot of land for a school in his village, When he was asked to give dimensions of the plot, he told that  if its length is decreased by $50 m$ and breadth is increased by $50 m$,then its area will remain same, but if length is decreased by $10 m$ and breadth is decreased by $20 m$, then its area will decrease by $5300 m^ 2 $  Using matrices, find the dimensions of the plot. Also give reason  why he wants to donate the plot for a school.
\item Solve the differential equation : \begin{align*}2ye^{x/y}dx+[y-2xe^{x/y}]dy=0\end{align*}
\item Solve the differential equation : \begin{align*}(x+1)\frac{dy}{dx}-y=e^{3x}(x+1)^3\end{align*}.
\item Using integration find the area of the region ${(x,y):y^2 \leq 6 ax and x^2+y^2 \leq 16a^2}$.	
\item Determine the intervals in which the function $f(x)$=$x^4-8x^3+22x^2-24x+21$ is strictly increasing (or) strictly decreasing.
\item Find the maximum and minimum values of $f(x) =\sec+\log\cos^2(x)$, $0<x<2\pi$.
\item Using properties of determinants, prove that: 
$\mydet{ 
(b+c)^2 & a^2 & bc \\ 
(c+a)^2 & b^2 & ca \\ 
(a+b)^2 & c^2 & ab } =
(a-b)(b-c)(c-a)(a+b+c)(a^2+b^2+c^2)
$
\item Using elementary row operations, find the inverse of the following matrix : ${A}= \myvec{2&-1&3\\-5&3&1\\-3&2&3}$
\item Three numbers are selected at random (without replacement) from first six positive integers. If $X$ denotes the smallest of the three numbers obtained, find the probability distribution of $X$. Also find the mean and variance of the distribution.
\item $A$ diet is to contain at least $80$ units of Vitamin $A$ and $100$ Units of minerals. Two foods $F_1$ and $F_2$ are available costing \rupee$5$ per unit and \rupee$6$ per unit respectively. One unit of food $F_1$contains $4$ $units$ of vitamin $A$ and $3$ units of minerals whereas one unit of food $F_2$ contains $3$ units of vitamin $A$ and $6$ units of minerals. Formulate this as a linear programming problem. Find the minimum cost of diet that consists of mixture of these two foods and also meets minimum nutritional requirement.
\item  Find the equation of the plane containing two parallel lines  $\frac{x-1}{2}=\frac{y+1}{-1}=\frac{z}{3}$ and $\frac{x}{4}=\frac{y-2}{-2}=\frac{z+1}{6}.$ Also, find if the plane thus obtained contains  the line $\frac{x-2}{3}=\frac{y-1}{1}=\frac{z-2}{5}$ or not.
\item Let $f : N \rightarrow N$ be a function defined as $f(x)= 4x^{2}+12x+15$.Show that $f:N \rightarrow S$ is invertible( where S is range of $f$).Find the inverse of $f$ and hence find $f^{-1}(31)$ and $f^{-1}(87)$.
\end{enumerate}
\end{document}

